---
title: "Procesamiento parcela 1"
output: html_notebook
---

Ver enlaces:

Raster 04: Work With Multi-Band Rasters - Image Data in R

http://neondataskills.org/R/Multi-Band-Rasters-In-R/

http://zevross.com/blog/2014/07/16/mapping-in-r-using-the-ggplot2-package/

https://github.com/bleutner/RStoolbox/issues/21

https://gis.stackexchange.com/questions/237180/using-a-fixed-palette-range-to-plot-an-ndvi-raster-in-r

Para la parcela 1 se utilizó una única imagen del vuelo Alamala 13122017 debido a que fue imposible generar los productos fotogramétricos mediante SfM.


```{r}
# required libraries

library("RStoolbox")
library("raster")
library("rgdal")
library("ggplot2")
library("SDMTools")

```


```{r}
# load tif using stack function instead raster

TTC08257_modified.stack <- stack("../../6_qgis/output/TTC08257_modified.tif")
class(TTC08257_modified.stack)

```


```{r}
# load parcela 1

parcelas <- readOGR("../../6_qgis/input/alamala.kml", "alamala")[0]

nrowdim <- dim(parcelas@data)
parcelas@data$id <- c(rep(1:nrowdim))
parcela1 <- subset(parcelas, parcelas@data$id %in% c(1,2))
class(parcela1)
plot(parcela1)

```




```{r}
parcela1.df <- fortify(parcela1) # to plot with ggplot
head(parcela1.df)
```

```{r}


# Set all pixels to NA, where bands are 0 (remove black background)
# Check if results are affected
# instead use crop and mask together (ver más adelante)

TTC08257_modified.stack[TTC08257_modified.stack[,] == 0] <- NA


# plot scene using ggRGB (from ggplot and RStoolbox)
ggRGB(TTC08257_modified.stack, r = 1, g = 2, b = 3, maxpixels = 2e+05, stretch="none", geom_raster = TRUE) + 
    geom_path(data = parcela1.df, aes(x = long, y = lat, group = group), size = 1, col="#fbae3b") +
    coord_equal() +
    theme_bw()
```

```{r}
ggsave("figures/parcela1.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```


Extraemos las parcelas

```{r}
# crop and mask whole area
 TTC08257_modified.stack_p1 <- crop(mask(TTC08257_modified.stack, parcela1),parcela1)

```



```{r}

# crop parcela 1.1

parcela11 <- subset(parcelas, parcelas@data$id %in% c(1))
TTC08257_modified.stack_p11 <- crop(mask(TTC08257_modified.stack, parcela11), parcela11)
 
# crop parcela 1.2
parcela12 <- subset(parcelas, parcelas@data$id %in% c(2))

TTC08257_modified.stack_p12 <- crop(mask(TTC08257_modified.stack, parcela12), parcela12)

```


Plot parcels

```{r}

ggRGB(TTC08257_modified.stack_p1, r = 1, g = 2, b = 3) + 
    geom_path(data = parcela1.df, aes(x = long, y = lat, group = group), size = 1, col="#fbae3b") +
    theme_bw()
```

Plot parcel 1.1

```{r}
p11 <- subset(parcela1.df, id == 0)

ggRGB(TTC08257_modified.stack_p11, r = 1, g = 2, b = 3) + 
    geom_path(data = p11, aes(x = long, y = lat, group = group), size = 1, col="#fbae3b") +
    labs(x="", y="", title="Parcela 1.1") +
   # coord_equal(ylim = c(min(p11$lat), max(p11$lat)), xlim= c(min(p11$long), max(p11$long))) +
    theme_bw() + 
    theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))  # make title bold and add spac

```


```{r}
ggsave("figures/parcela1_1.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```


Plot parcel 1.2

```{r}

p12 <- subset(parcela1.df, id == 1)


ggRGB(TTC08257_modified.stack_p12, r = 1, g = 2, b = 3) + 
    geom_path(data = p12, aes(x = long, y = lat, group = group), size = 1, col="#fbae3b") +
    labs(x="", y="", title="Parcela 1.2")+
    coord_equal(ylim = c(min(p12$lat), max(p12$lat)), xlim= c(min(p12$long), max(p12$long))) +
    theme_bw() + 
    theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))  # make title bold and add spac

```

```{r}
ggsave("figures/parcela1_2.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

Calculate VIs

```{r}

p11.VIs <- spectralIndices(TTC08257_modified.stack_p11, red=2, nir =1, indices=c("NDVI", "MSAVI2", "DVI"))
breaks <- seq(0, 1, by=0.01)

plot(p11.VIs)
```

Plot VI one by one


NDVI Parcela 1.1

```{r}
cols <- colorRampPalette(c("red", "yellow", "lightgreen"))(length(breaks)-1)
ggR(p11.VIs$NDVI, geom_raster = TRUE) +
  labs(x="", y="", title= "Parcela 1.1") +
  scale_fill_gradientn(colours=cols,  na.value=NA) + 
  theme_bw() +
  theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))

```

And save

```{r}
ggsave("figures/parcela1_1_NDVI.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

MSAVI2 Parcela 1.1

```{r}
cols <- colorRampPalette(c("red", "yellow", "lightgreen"))(length(breaks)-1)
ggR(p11.VIs$MSAVI2, geom_raster = TRUE) +
  labs(x="", y="", title= "Parcela 1.1") +
  scale_fill_gradientn(colours=cols,  na.value=NA) + 
  theme_bw() +
  theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))

```

And save

```{r}
ggsave("figures/parcela1_1_MSAVI2.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

DVI Parcela 1.1

```{r}
cols <- colorRampPalette(c("red", "yellow", "lightgreen"))(length(breaks)-1)
ggR(p11.VIs$DVI, geom_raster = TRUE) +
  labs(x="", y="", title= "Parcela 1.1") +
  scale_fill_gradientn(colours=cols,  na.value=NA) + 
  theme_bw() +
  theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))

```


```{r}
ggsave("figures/parcela1_1_DVI.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

Again with p1.2

```{r}
p12.VIs <- spectralIndices(TTC08257_modified.stack_p12, red=2, nir =1, indices=c("NDVI", "MSAVI2", "DVI"))
breaks <- seq(0, 1, by=0.01)

plot(p12.VIs)
```

```{r}
ggR(p12.VIs$NDVI, geom_raster = TRUE) +
  labs(x="", y="", title="Parcela 1.2") +
  scale_fill_gradientn(colours=cols,  na.value=NA) + 
  theme_bw() +
  theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))  # make title bold and add spac

```

```{r}
ggsave("figures/parcela1_2_NDVI.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

MSAVI2 Parcela 1.2

```{r}
ggR(p12.VIs$MSAVI2, geom_raster = TRUE) +
  labs(x="", y="", title="Parcela 1.2") +
  scale_fill_gradientn(colours=cols,  na.value=NA) + 
  theme_bw() +
  theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))  # make title bold and add spac

```

Save

```{r}
ggsave("figures/parcela1_2_MSAVI2.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

DVI Parcela 1.2

```{r}
ggR(p12.VIs$DVI, geom_raster = TRUE) +
  labs(x="", y="", title="Parcela 1.2") +
  scale_fill_gradientn(colours=cols,  na.value=NA) + 
  theme_bw() +
  theme(plot.title = element_text(lineheight=.8, face="bold", vjust=1, hjust = 0.5))  # make title bold and add spac

```

Save

```{r}
ggsave("figures/parcela1_2_DVI.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

### Exploratory data analysis of Vegetation Indices


Bind indices in a whole dataframe

```{r}
library(dplyr)
library(plyr) # Tools for Splitting, Applying and Combining Data

raster_to_df <- function(x) {
  stack(as.data.frame(x))
} # convert raster to dataframe


l<- list(p11 = p11.VIs, p12 = p12.VIs)

l.df <- lapply(X = l, FUN = raster_to_df) # list of data frames


l.df.VIs <- ldply(l.df ,rbind) # Split list, apply function, and return results in a data frame.


```

Plot NDVI box-plot

```{r}
l.df.VIs.NDVI <-  subset(l.df.VIs, ind == "NDVI" )
ggplot(l.df.VIs.NDVI) + 
  geom_boxplot(aes(x = .id, y = values, colour=.id)) +
  facet_grid(. ~ ind) +
  theme_bw()
```



```{r}
ggsave("figures/boxplot_p11_p12_NDVI.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

Plot MSAVI2 box-plot

```{r}
l.df.VIs.MSAVI2 <-  subset(l.df.VIs, ind == "MSAVI2" )
ggplot(l.df.VIs.MSAVI2) + 
  geom_boxplot(aes(x = .id, y = values, colour=.id)) +
  facet_grid(. ~ ind) +
  theme_bw()
```


```{r}
ggsave("figures/boxplot_p11_p12_MSAVI2.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```

Plot DVI box-plot

```{r}
l.df.VIs.DVI <-  subset(l.df.VIs, ind == "DVI" )
ggplot(l.df.VIs.DVI) + 
  geom_boxplot(aes(x = .id, y = values, colour=.id)) +
  facet_grid(. ~ ind) +
  theme_bw()
```

```{r}
ggsave("figures/boxplot_p1_p2_DVI.png", 
 plot = last_plot(), # or give ggplot object name as in myPlot,
 width = 5, height = 5, 
 units = "in", # other options c("in", "cm", "mm"), 
 dpi = 300)
```


### Classification

Play a little with other functions

```{r}
## Run classification
set.seed(25)
unC <- unsuperClass(TTC08257_modified.stack_p11, nSamples = 100, nClasses = 2, nStarts = 5)
unC
plot(unC$map)
```

```{r}
PatchStat(TTC08257_modified.stack_p11$TTC08257_modified.1, cellsize = 1, latlon = FALSE)
```



